I can see clearly now: reinterpreting statistical significance

### 2018-10-09 doc.tex

In a meta-analysis of 356 studies \citet{Bernardietal.2017} found that 72\% of studies contained an ambiguous use of the term ``significant'', 49\% interpreted non-significant effects as zero effects, and 44\% failed to report a comprehensible effect size. The misuse and misinterpretation of NHST is so frequent that there have been recent calls for drastically reducing \citep{SzucsandIoannidis2017} or abandoning \citep{McShaneetal.2017} its use. Other prescriptions have included the complete abandonment of frequentist statistics \citeneeded, or the use of a stricter significance threshold (e.g. $p < 0.005$: \citealt{Benjaminetal.2018}); however, the former seems impractical, while the latter is unlikely to reduce the misuse and misinterpretation of \pvals, or the publication bias imposed by any \pval threshold \citep{Ridleyetal.2007}.

@@

In most biological studies, the null hypothesis is known or believed to not be strictly true.
Even in cases where the null hypothesis is sensible (e.g., particle physics) \pval testing does not provide a route to confirmation.
This being the case, it is worth asking how NHST has survived `` if it is as idiotic as \ldots long believed''. 
\jd{Why does Morgan cite Kramer?} \citet{Kramer2011}.

@@

The language of ``statistical clarity'' could help researchers escape various logical traps while interpreting the results of NHST, allowing for the continued use of NHST as a simple, robust method of evaluating whether a data signal is clear (see \citealt{Abelson1997} for arguments for NHST \bmb{what's in Abelson? How much of our argument do they anticipate?}).
The use of ``significance'' to describe the results of hypothesis tests is deeply, and sometimes subtly, misleading, because it is at odds with other meanings of the word: the \pval is not an accurate gauge of whether a result is large in magnitude, biologically important, or relevant. ``Clarity,'' on the other hand, is an apt term for what NHST actually evaluates. 
\citet{jones2000sensible} and \citet{robinson2001past} suggest that researchers should report $p > 0.05$ using language such as ``the direction of the differences among the treatments was undetermined''. This is a step in the right direction. 
Replacing ``significance'' with ``clarity'' takes this further, and has the promise to substantially improve statistical communication.

>>>>

In a meta-analysis of 356 studies \citet{Bernardietal.2017} found that 72\% of studies contained an ambiguous use of the term ``significant'', 49\% interpreted non-significant effects as zero effects, and 44\% failed to report a comprehensible effect size. The misuse and misinterpretation of NHST is so frequent that there have been recent calls for drastically reducing \citep{SzucsandIoannidis2017} or abandoning \citep{McShaneetal.2017} its use. Other prescriptions have included the complete abandonment of frequentist statistics \citep{The2011}, or the use of a stricter significance threshold (e.g. $p < 0.005$: \citealt{Benjaminetal.2018}); however, the former seems impractical, while the latter is unlikely to reduce the misuse and misinterpretation of \pvals, or the publication bias imposed by any \pval threshold \citep{Ridleyetal.2007}.

@@

In most biological studies, the null hypothesis is known or believed to not be strictly true.
Even in cases where the null hypothesis is sensible \citep[e.g., particle physics][]{Staley2017} \pval testing does not provide a route to confirmation.
This being the case, it is worth asking how NHST has survived ``if it is as idiotic as \ldots long believed''. 
\jd{Why does Morgan cite Kramer?} \citet{Kramer2011}.

@@

The language of ``statistical clarity'' could help researchers escape various logical traps while interpreting the results of NHST, allowing for the continued use of NHST as a simple, robust method of evaluating whether a data signal is clear (see \citealt{Abelson1997} for arguments for NHST \bmb{what's in Abelson? How much of our argument do they anticipate?}).
The use of ``significance'' to describe the results of hypothesis tests is deeply, and sometimes subtly, misleading, because it is at odds with other meanings of the word: the \pval is not an accurate gauge of whether a result is large in magnitude, biologically important, or relevant. ``Clarity,'' on the other hand, is an apt term for what NHST actually evaluates. 
\citet{jones2000sensible} and \citet{robinson2001past} suggest that researchers should report $p > 0.05$ using language such as ``the direction of the differences among the treatments was undetermined''. This is a step in the right direction. 
Replacing ``significance'' with ``clarity'' takes this idea further, and has the promise to substantially improve statistical communication.
